Interval Probability for Fuzzy Quantum Theories

### 2016-07-21 prob.tex
prob.tex Upgrading to BibLaTeX to handle translated sources correctly...
prob.tex Fix the bug about using BibTeX with BibLaTeX...
prob.tex Fix BibLaTeX so that it works when import to LyX...
prob.tex \subsection{Real-Valued Probability Spaces} Updated...

\documentclass{article}
\usepackage{fullpage}
\usepackage{url}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{wesa}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

@@

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)=1$.
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure, or just called the Radon-Nikodym derivative
of $\pmeas$ because we are always with respect to the counting measure.
The Radon-Nikodym theorem states that the converse is also true.

\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}]
For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
derivative~$\rho$ such that equation~(\ref{eq:Radon-Nikodym})
holds.\qed\end{thm}

@@

\bibliographystyle{unsrt}
\bibliography{discreteGBKS}

>>>>

\documentclass{article}
\usepackage[ backend=biber,sorting=none]{biblatex}
\addbibresource{discreteGBKS.bib}
\usepackage{fullpage}
\usepackage{url}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{wesa}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

@@

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)=1$.
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure~\cite{Nikodym1930,Folland2013}, or just
called the Radon-Nikodym derivative of $\pmeas$ because we are always
with respect to the counting measure. The Radon-Nikodym theorem states
that the converse is also true.

\begin{thm}[Radon-Nikodym theorem for finite probability space~\cite{Kolmogorov1950,Swart2013}]
For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
derivative~$\rho$ such that equation~(\ref{eq:Radon-Nikodym})
holds.\qed\end{thm}

@@

\printbibliography
